---
title: "codebook"
author: "Ahmed"
date: "2023-08-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Codebook
This is the codebook for Step 5 in the assignment
The raw data was collected from the downloaded zip file provided for the assignment. This dataset includes both test and train datasets.
Using grep, I was able to grab all the mean and std columns I needed for processing
Then, I built a table for the data
I appended the subject and activity columns to the data
I called on mean function, grouped by subject,activity





```{r }
View(read.table(file.path("data","averages.txt"),header = TRUE))
```

## What do the table columns mean?
**subject**: A number from 1 to 30. Refers to the subject used in the expirment
**activity**: The activity from which the data was collected:
WALKING
WALKING_UPSTAIRS
WALKING_DOWNSTAIRS
SITTING
STANDING
LAYING

The following columns refer to the average of the measurement collected:
**avg**: signifies this is the average of multiple readings
**...**: name of measurement
**mean/std**: tells you which kind of measurment taken (mean or std)
**x,y,z**: which axis the measurement was taken

```{r}
Columns<-names(read.table(file.path("data","averages.txt"),header = TRUE))
View(data.frame(Columns))
```

